Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-04-17 IJCAR2020/related.tex
Removed redundancy about their approach.

Concerning the formalization of the method 
of forcing, all of the previous works (to the best of our knowledge)
have been done interpreting set theory into type theory, and
none of them uses the ctm approach. The
most important is the recent \emph{Flypitch} project  by 
Han and van Doorn
\cite{han_et_al:LIPIcs:2019:11074,DBLP:conf/cpp/HanD20}, which includes
a formalization of the independence of $\CH$ by means of
the Boolean-valued approach to forcing, using the Lean
proof assistant. The Flypitch
formalization is largely orthogonal to ours, and this
precludes a direct comparison of code. But we can
highlight some conceptual differences between our development and the
corresponding fraction of Flypitch.

>>>>

Concerning the formalization of the method of forcing, to the best of
our knowledge there is only another one that deals with forcing for
set theory: the recent \emph{Flypitch} project by Han and van Doorn
\cite{han_et_al:LIPIcs:2019:11074,DBLP:conf/cpp/HanD20}, which
includes a formalization of the independence of CH by means of the
Boolean-valued approach to forcing, using the Lean proof
assistant. The Flypitch formalization is largely orthogonal to ours
(it is based on Boolean-valued models, which are interpreted into
type theory through a variant of the Aczel encoding of set theory),
and this precludes a direct comparison of code. But we can highlight
some conceptual differences between our development and the
corresponding fraction of Flypitch.
